---
title: "Obesity project"
author: "Rodrigo Delibnerato"
date: "4/10/2018"
output: word_document
---

## Data visualization, transformation and assessing normality

```{r transformation}

total_rod$ethnicity<-as.factor(total_rod$ethnicity)
total_rod$hospitaladmitsource<-as.factor(total_rod$hospitaladmitsource)
total_rod$hospitaladmityear<-as.factor(total_rod$hospitaladmityear)
total_rod$unittype<-as.factor(total_rod$unittype)
total_rod$unitadmitsource<-as.factor(total_rod$unitadmitsource)
total_rod$apacheadmissiondx<-as.factor(total_rod$apacheadmissiondx)
total_rod$hospitalid<-as.factor(total_rod$hospitalid)

hist(total_rod$age_fixed)
hist(total_rod$height)
hist(total_rod$weight)
hist(total_rod$bmi)
hist(total_rod$charlson_score)
hist(total_rod$sofatotal)
hist(total_rod$apachescore)


with(total_rod , qqnorm((age_fixed)))
with(total_rod , qqnorm((height)))
with(total_rod , qqnorm((weight)))
with(total_rod , qqnorm((bmi)))
with(total_rod , qqnorm((charlson_score)))
with(total_rod , qqnorm((sofatotal)))
with(total_rod , qqnorm((apachescore)))

summary(total_rod)

```

## Subsetting the data in using the bmi_group:
   underweight
   normal
   overweight
   obese
   morbid obesity
```{r subseting}


under<-subset(total_rod, bmi_group == 1)

normal<-subset(total_rod,bmi_group == 2)

over<-subset(total_rod, bmi_group == 3)

obese<-subset(total_rod, bmi_group == 4)

morbid<-subset(total_rod, bmi_group == 5)

```

##Table 1 - manuscript

https://github.com/kaz-yos/tableone

https://www.r-bloggers.com/table-1-and-the-characteristics-of-study-population/

https://www.rdocumentation.org/packages/tableone/versions/0.8.1/topics/print.TableOne

http://rstudio-pubs-static.s3.amazonaws.com/13321_da314633db924dc78986a850813a50d5.html
```{r Table 1}

##data preparation for Table 1

#adjusting ethnicity
total_rod$ethnicity<-as.factor(total_rod$ethnicity)

#transforming apache comorbidities in numeric values to create the apache_n_comorbidity variable

total_rod$aids<-as.numeric(as.character(total_rod$aids))
total_rod$hepaticfailure<-as.numeric(as.character(total_rod$hepaticfailure))
total_rod$lymphoma<-as.numeric(as.character(total_rod$lymphoma))
total_rod$metastaticcancer<-as.numeric(as.character(total_rod$metastaticcancer))
total_rod$leukemia<-as.numeric(as.character(total_rod$leukemia))
total_rod$immunosuppression<-as.numeric(as.character(total_rod$immunosuppression))
total_rod$diabetes<-as.numeric(as.character(total_rod$diabetes))
total_rod$cirrhosis<-as.numeric(as.character(total_rod$cirrhosis))

total_rod$apache_n_comorbidity<-NA
total_rod$apache_n_comorbidity<-total_rod$aids+total_rod$hepaticfailure+total_rod$lymphoma+total_rod$metastaticcancer+total_rod$leukemia+total_rod$immunosuppression+total_rod$diabetes+total_rod$cirrhosis
total_rod$apache_n_comorbidity<- as.factor(total_rod$apache_n_comorbidity)

#adjusting unittype
total_rod$unidades<-NA
total_rod$unidades[total_rod$unittype=="CCU-CTICU"]<-"Cardiac ICU"
total_rod$unidades[total_rod$unittype=="CSICU"]<-"Cardiac ICU"
total_rod$unidades[total_rod$unittype=="CTICU"]<-"Cardiac ICU"
total_rod$unidades[total_rod$unittype=="Cardiac ICU"]<-"Cardiac ICU"
total_rod$unidades[total_rod$unittype=="Med-Surg ICU"]<-"Mixed ICU"
total_rod$unidades[total_rod$unittype=="MICU"]<-"MICU"
total_rod$unidades[total_rod$unittype=="Neuro ICU"]<-"Neuro ICU"
total_rod$unidades[total_rod$unittype=="SICU"]<-"Surgical ICU"
total_rod$unidades<-as.factor(total_rod$unidades)

#adjusting unitadmitsource
total_rod$unitadmitsource<-as.factor(total_rod$unitadmitsource)
total_rod$unidadedeadmissao<-total_rod$unitadmitsource
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Acute Care/Floor"]<-"Floor"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Chest Pain Center"]<-"Emergency Department"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Direct Admit"]<-"Emergency Department"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Emergency Department"]<-"Emergency Department"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Floor"]<-"Floor"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "ICU"]<-"Other"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "ICU to SDU"]<-"Other"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Observation"]<-"Emergency Department"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Operating Room"]<-"Operating Room"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Other"]<-"Other"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Other Hospital"]<-"Other"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Other ICU"]<-"Other"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "PACU"]<-"Operating Room"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Recovery Room"]<-"Operating Room"
total_rod$unidadedeadmissao[total_rod$unidadedeadmissao== "Step-Down Unit (SDU)"]<-"Other"
total_rod$unidadedeadmissao<-as.factor(total_rod$unidadedeadmissao)

total_rod$diedinhospital<-as.factor(total_rod$diedinhospital)

## Making Table 1
library(tableone)
require(ReporteRs)
require(magrittr)


listVars<- c("age_fixed","gender","ethnicity","bmi","apache_n_comorbidity","charlson_score",  "unidadedeadmissao", "unidades","region","numbedscategory","teachingstatus", "electivesurgery","sofatotal", "apachescore","oasis","intubated_first_24h","real_icu_los","real_hospital_los","diedinhospital")

catVars<-c("gender","ethnicity", "unidadedeadmissao","apache_n_comorbidity", "unidades","region","numbedscategory","teachingstatus","electivesurgery","intubated_first_24h","diedinhospital")

table1 <- CreateTableOne(vars = listVars, data = total_rod, factorVars = catVars,testNormal=oneway.test, strata = c("bmi_group"))

table1<-print(table1,nonnormal=c("sofatotal", "apachescore","real_icu_los","real_hospital_los"),testApprox=c("gender","ethnicity", "unidadedeadmissao", "unidades","region","numbedscategory","teachingstatus","electivesurgery","intubated_first_24h","diedinhospital"))

docx( ) %>% 
     addFlexTable(table1 %>%
     FlexTable(header.cell.props = cellProperties( background.color = "#003366"),
               header.text.props = textBold( color = "white" ),
               add.rownames = TRUE ) %>%
               setZebraStyle( odd = "#DDDDDD", even = "#FFFFFF" ) ) %>%
     writeDoc(file = "table1_03042018.docx")

browseURL("table1_03042018.docx") #wordfile


```

## transforming diedinhospita from factor to numerical (again)

```{r factor_to_numeric}

total_rod$diedinhospital<-as.numeric(as.character(total_rod$diedinhospital))

```

## Creating the four new models using Logistic Regression: 

   - r-AIV (APACHE IV recalibrated)
   - r-OASIS (OASIS recalibrated)
   - r-AIV-BMI (APACHE IV recalibrated with BMI)
   - r-OASIS-BMI (OASIS recalibrated with BMI)

How?
1. Splitting training and test
 - we decided to divide it by hospitals: from the total of 189 hospital in our final cohort, we split it (50/50) in different hospitals. So each new cohort will be formed from different hospital
 
2. classifiers creation - 4 new classifiers for each new model

```{r splitting training and test set }


apache_models<-total_rod[,c(18,65,70,68)] # hospitalid, original apache predictions, bmi_group,diedinhospital
oasis_models <-total_rod [,c(18,67,70,68)] # hospitalid, original oasis prediction, bmi_group, diedinhospital


apache_training_set <- subset (apache_models, apache_models$hospitalid > 258)# subsetting 50% of the hospital 
apache_test_set <- subset (apache_models, apache_models$hospitalid < 259)# subsetting 50% of the hospital 

oasis_training_set <- subset (oasis_models, oasis_models$hospitalid > 258)# subsetting 50% of the hospital 
oasis_test_set <- subset (oasis_models, oasis_models$hospitalid < 259)# subsetting 50% of the hospital 

## Now, let`s create 4 new classifiers in the training set:

  -- 1.  fit=apache_predicted_recalib            (apache recalibration + BMI)
  -- 2.  fit.null=apache_predicted_recalib_null  (apache just recalibration)
  -- 3.  fit2=oasis_predicted_recalib            (oasisrecalibration + BMI)
  -- 4.  fit.null2=oasis_predicted_recalib_null  (oasis just recalibration)

## 1. classifier for the model recalibration APACHE + BMI (r-AIV-BMI)

logit <- function(x) {
	return(log(x/(1-x)))
}

fit <- glm(diedinhospital ~ offset(logit(predictedhospitalmortality)) 
           + bmi_group,data=apache_training_set,family="binomial")

 

## 2. classifier for the model recalibration APACHE (r-AIV)

logit <- function(x) {
	return(log(x/(1-x)))
}

fit.null <- glm(diedinhospital ~ offset(logit(predictedhospitalmortality)) 
                ,data=apache_training_set,family="binomial")


## 3.classifier for the  model recalibration OASIS +BMI (r-OASIS-BMI)

logit <- function(x) {
	return(log(x/(1-x)))
}

fit2 <- glm(diedinhospital ~ offset(logit(oasis_prob)) + bmi_group,   
            data=oasis_training_set,family="binomial")



## 4.  classifier for the model recalibration OASIS (r-OASIS)

logit <- function(x) {
	return(log(x/(1-x)))
}

fit.null2 <- glm(diedinhospital ~ offset(logit(oasis_prob)),
                 data=oasis_training_set,family="binomial")

 
```

## Adding the prediction (made in the training set) into the Test Set

```{r adding predction into the test set}

 apache_test_set$apache_predicted_recalib<-NA
 apache_test_set$apache_predicted_recalib <- predict(fit, type='response', 
                                                     newdata=apache_test_set) 
 apache_test_set$apache_predicted_recalib_null <- NA
 apache_test_set$apache_predicted_recalib_null <- predict(fit.null, type= 'response',
                                                          newdata = apache_test_set)

 oasis_test_set$oasis_predicted_recalib <- NA
 oasis_test_set$oasis_predicted_recalib <- predict(fit2, type='response',
                                                   newdata = oasis_test_set)

 oasis_test_set$oasis_predicted_recalib_null <- NA
 oasis_test_set$oasis_predicted_recalib_null <- predict(fit.null2, type= 'response',
                                                        newdata = oasis_test_set)

```

## Splitting TEST SET into BMI categories

```{r splitting}

apache_under_test<-subset(apache_test_set, bmi_group == 1)
oasis_under_test<-subset(oasis_test_set, bmi_group == 1)

apache_normal_test<-subset(apache_test_set,bmi_group == 2)
oasis_normal_test<-subset(oasis_test_set,bmi_group == 2)

apache_over_test<-subset(apache_test_set, bmi_group ==3)
oasis_over_test<-subset(oasis_test_set, bmi_group ==3)

apache_obese_test<-subset(apache_test_set, bmi_group ==4)
oasis_obese_test<-subset(oasis_test_set, bmi_group ==4)

apache_morbid_test<-subset(apache_test_set, bmi_group ==5)
oasis_morbid_test<-subset(oasis_test_set, bmi_group ==5)

```

## Assessing the original model APACHE performance, per BMI_group, in the testing set!!!

```{r}
library (pROC)

## Making AUC and ci.AUC for original APACHE per BMI category, in the testing set!!!

roc_total<-roc(apache_test_set$diedinhospital, apache_test_set$predictedhospitalmortality)
auc(roc_total)
ci.auc(roc_total)

roc_under<-roc(apache_under_test$diedinhospital, apache_under_test$predictedhospitalmortality)
auc(roc_under)
ci.auc(roc_under)

roc_normal<-roc(apache_normal_test$diedinhospital, apache_normal_test$predictedhospitalmortality)
auc(roc_normal)
ci.auc(roc_normal)

roc_over<-roc(apache_over_test$diedinhospital, apache_over_test$predictedhospitalmortality)
auc(roc_over)
ci.auc(roc_over)

roc_obese<-roc(apache_obese_test$diedinhospital, apache_obese_test$predictedhospitalmortality)
auc(roc_obese)
ci.auc(roc_obese)

roc_morbid<-roc(apache_morbid_test$diedinhospital, apache_morbid_test$predictedhospitalmortality)
auc(roc_morbid)
ci.auc(roc_morbid)

# Making SMR and 95% CI for original APACHE per BMI category

library(ems)

apache_test_set$diedinhospital<-as.numeric(as.character(apache_test_set$diedinhospital))
apache_test_set$bmi_group<-as.factor(apache_test_set$bmi_group)


SMR (apache_test_set$diedinhospital, apache_test_set$predictedhospitalmortality, digits = 2)
SMR (apache_under_test$diedinhospital, apache_under_test$predictedhospitalmortality, digits = 2)
SMR (apache_normal_test$diedinhospital, apache_normal_test$predictedhospitalmortality, digits = 2)
SMR (apache_over_test$diedinhospital, apache_over_test$predictedhospitalmortality, digits = 2)
SMR (apache_obese_test$diedinhospital, apache_obese_test$predictedhospitalmortality, digits = 2)
SMR (apache_morbid_test$diedinhospital, apache_morbid_test$predictedhospitalmortality, digits = 2)

```


## Making AUC and ci.AUCand SMR (95%CI) for original OASIS per BMI category, in the testing set!!!

```{r}


library (pROC)

## Making AUC and ci.AUC for original OASIS per BMI category, in the testing set!!!

roc_total1<-roc(oasis_test_set$diedinhospital, oasis_test_set$oasis_prob)
auc(roc_total1)
ci.auc(roc_total1)

roc_under1<-roc(oasis_under_test$diedinhospital, oasis_under_test$oasis_prob)
auc(roc_under1)
ci.auc(roc_under1)

roc_normal1<-roc(oasis_normal_test$diedinhospital, oasis_normal_test$oasis_prob)
auc(roc_normal1)
ci.auc(roc_normal1)

roc_over1<-roc(oasis_over_test$diedinhospital, oasis_over_test$oasis_prob)
auc(roc_over1)
ci.auc(roc_over1)

roc_obese1<-roc(oasis_obese_test$diedinhospital, oasis_obese_test$oasis_prob)
auc(roc_obese1)
ci.auc(roc_obese1)

roc_morbid1<-roc(oasis_morbid_test$diedinhospital, oasis_morbid_test$oasis_prob)
auc(roc_morbid1)
ci.auc(roc_morbid1)


# Making SMR and 95% CI for original OASIS per BMI category

library(ems)

oasis_test_set$diedinhospital<-as.numeric(as.character(oasis_test_set$diedinhospital))
oasis_test_set$bmi_group<-as.factor(oasis_test_set$bmi_group)


SMR (oasis_test_set$diedinhospital, oasis_test_set$oasis_prob, digits = 2)
SMR (oasis_under_test$diedinhospital, oasis_under_test$oasis_prob, digits = 2)
SMR (oasis_normal_test$diedinhospital, oasis_normal_test$oasis_prob, digits = 2)
SMR (oasis_over_test$diedinhospital, oasis_over_test$oasis_prob, digits = 2)
SMR (oasis_obese_test$diedinhospital, oasis_obese_test$oasis_prob, digits = 2)
SMR (oasis_morbid_test$diedinhospital, oasis_morbid_test$oasis_prob, digits = 2)



```

## Assessing the performance of these two new models in the TEST SET, according to the BMI category

1. Discrimination: AUROC (95% CI)
2. Calibration:
    a.SMR (95% CI) -- http://www.openepi.com/SMR/SMR.htm 
    b.calibration belt plot
    
 ## For APACHE + BMI model

```{r}

## Calculating AUROC APACHE IV + BMI -- > r-AIV-BMI

library (pROC)

roc_total2<-roc(apache_test_set$diedinhospital, apache_test_set$apache_predicted_recalib)
auc(roc_total2)
ci.auc(roc_total2)

roc_under2<-roc(apache_under_test$diedinhospital, apache_under_test$apache_predicted_recalib)
auc(roc_under2)
ci.auc(roc_under2)

roc_normal2<-roc(apache_normal_test$diedinhospital, apache_normal_test$apache_predicted_recalib)
auc(roc_normal2)
ci.auc(roc_normal2)

roc_over2<-roc(apache_over_test$diedinhospital, apache_over_test$apache_predicted_recalib)
auc(roc_over2)
ci.auc(roc_over2)

roc_obese2<-roc(apache_obese_test$diedinhospital, apache_obese_test$apache_predicted_recalib)
auc(roc_obese2)
ci.auc(roc_obese2)

roc_morbid2<-roc(apache_morbid_test$diedinhospital, apache_morbid_test$apache_predicted_recalib)
auc(roc_morbid2)
ci.auc(roc_morbid2)

# Making SMR and 95% CI for APACHE + BMI (r-AIV-BMI) per BMI category

library(ems)

apache_test_set$diedinhospital<-as.numeric(as.character(apache_test_set$diedinhospital))
apache_test_set$bmi_group<-as.factor(apache_test_set$bmi_group)


SMR (apache_test_set$diedinhospital, apache_test_set$apache_predicted_recalib, digits = 2)
SMR (apache_under_test$diedinhospital, apache_under_test$apache_predicted_recalib, digits = 2)
SMR (apache_normal_test$diedinhospital, apache_normal_test$apache_predicted_recalib, digits = 2)
SMR (apache_over_test$diedinhospital, apache_over_test$apache_predicted_recalib, digits = 2)
SMR (apache_obese_test$diedinhospital, apache_obese_test$apache_predicted_recalib, digits = 2)
SMR (apache_morbid_test$diedinhospital, apache_morbid_test$apache_predicted_recalib, digits = 2)




```

## For APACHE IV recalibrated (without BMI) -> r-AIV

```{r}

#AUROC for APACHE IV (without BMI)-> r-AIV

library (pROC)

roc_total3<-roc(apache_test_set$diedinhospital, apache_test_set$apache_predicted_recalib_null)
auc(roc_total3)
ci.auc(roc_total3)

roc_under3<-roc(apache_under_test$diedinhospital, apache_under_test$apache_predicted_recalib_null)
auc(roc_under3)
ci.auc(roc_under3)

roc_normal3<-roc(apache_normal_test$diedinhospital, apache_normal_test$apache_predicted_recalib_null)
auc(roc_normal3)
ci.auc(roc_normal3)

roc_over3<-roc(apache_over_test$diedinhospital, apache_over_test$apache_predicted_recalib_null)
auc(roc_over3)
ci.auc(roc_over3)

roc_obese3<-roc(apache_obese_test$diedinhospital, apache_obese_test$apache_predicted_recalib_null)
auc(roc_obese3)
ci.auc(roc_obese3)

roc_morbid3<-roc(apache_morbid_test$diedinhospital, apache_morbid_test$apache_predicted_recalib_null)
auc(roc_morbid3)
ci.auc(roc_morbid3)

# Making SMR and 95% CI for APACHE (without BMI)-> r-AIV, per BMI category

library(ems)

apache_test_set$diedinhospital<-as.numeric(as.character(apache_test_set$diedinhospital))
apache_test_set$bmi_group<-as.factor(apache_test_set$bmi_group)


SMR (apache_test_set$diedinhospital, apache_test_set$apache_predicted_recalib_null, digits = 2)
SMR (apache_under_test$diedinhospital, apache_under_test$apache_predicted_recalib_null, digits = 2)
SMR (apache_normal_test$diedinhospital, apache_normal_test$apache_predicted_recalib_null, digits = 2)
SMR (apache_over_test$diedinhospital, apache_over_test$apache_predicted_recalib_null, digits = 2)
SMR (apache_obese_test$diedinhospital, apache_obese_test$apache_predicted_recalib_null, digits = 2)
SMR (apache_morbid_test$diedinhospital, apache_morbid_test$apache_predicted_recalib_null, digits = 2)


```

## For OASIS + BMI model --> r-OASIS-BMI

```{r}

#AUROC for OASIS + BMI model--> r-OASIS-BMI

library (pROC)

roc_total4<-roc(oasis_test_set$diedinhospital, oasis_test_set$oasis_predicted_recalib)
auc(roc_total4)
ci.auc(roc_total4)

roc_under4<-roc(oasis_under_test$diedinhospital, oasis_under_test$oasis_predicted_recalib)
auc(roc_under4)
ci.auc(roc_under4)

roc_normal4<-roc(oasis_normal_test$diedinhospital, oasis_normal_test$oasis_predicted_recalib)
auc(roc_normal4)
ci.auc(roc_normal4)

roc_over4<-roc(oasis_over_test$diedinhospital, oasis_over_test$oasis_predicted_recalib)
auc(roc_over4)
ci.auc(roc_over4)

roc_obese4<-roc(oasis_obese_test$diedinhospital, oasis_obese_test$oasis_predicted_recalib)
auc(roc_obese4)
ci.auc(roc_obese4)

roc_morbid4<-roc(oasis_morbid_test$diedinhospital, oasis_morbid_test$oasis_predicted_recalib)
auc(roc_morbid4)
ci.auc(roc_morbid4)

# Making SMR and 95% CI for OASIS + BMI--> r-OASIS-BMI, per BMI category

library(ems)

oasis_test_set$diedinhospital<-as.numeric(as.character(oasis_test_set$diedinhospital))
oasis_test_set$bmi_group<-as.factor(oasis_test_set$bmi_group)


SMR (oasis_test_set$diedinhospital, oasis_test_set$oasis_predicted_recalib, digits = 2)
SMR (oasis_under_test$diedinhospital, oasis_under_test$oasis_predicted_recalib, digits = 2)
SMR (oasis_normal_test$diedinhospital, oasis_normal_test$oasis_predicted_recalib, digits = 2)
SMR (oasis_over_test$diedinhospital, oasis_over_test$oasis_predicted_recalib, digits = 2)
SMR (oasis_obese_test$diedinhospital, oasis_obese_test$oasis_predicted_recalib, digits = 2)
SMR (oasis_morbid_test$diedinhospital, oasis_morbid_test$oasis_predicted_recalib, digits = 2)

```

## OASIS recalibration without BMI --> r-OASIS

```{r}

#AUROC for OASIS (without BMI)--> r-OASIS

library (pROC)

roc_total5<-roc(oasis_test_set$diedinhospital, oasis_test_set$oasis_predicted_recalib_null)
auc(roc_total5)
ci.auc(roc_total5)

roc_under5<-roc(oasis_under_test$diedinhospital, oasis_under_test$oasis_predicted_recalib_null)
auc(roc_under5)
ci.auc(roc_under5)

roc_normal5<-roc(oasis_normal_test$diedinhospital, oasis_normal_test$oasis_predicted_recalib_null)
auc(roc_normal5)
ci.auc(roc_normal5)

roc_over5<-roc(oasis_over_test$diedinhospital, oasis_over_test$oasis_predicted_recalib_null)
auc(roc_over5)
ci.auc(roc_over5)

roc_obese5<-roc(oasis_obese_test$diedinhospital, oasis_obese_test$oasis_predicted_recalib_null)
auc(roc_obese5)
ci.auc(roc_obese5)

roc_morbid5<-roc(oasis_morbid_test$diedinhospital, oasis_morbid_test$oasis_predicted_recalib_null)
auc(roc_morbid5)
ci.auc(roc_morbid5)

# Making SMR and 95% CI for OASIS (withour BMI)--> r-OASIS, per BMI category

library(ems)

oasis_test_set$diedinhospital<-as.numeric(as.character(oasis_test_set$diedinhospital))
oasis_test_set$bmi_group<-as.factor(oasis_test_set$bmi_group)


SMR (oasis_test_set$diedinhospital, oasis_test_set$oasis_predicted_recalib_null, digits = 2)
SMR (oasis_under_test$diedinhospital, oasis_under_test$oasis_predicted_recalib_null, digits = 2)
SMR (oasis_normal_test$diedinhospital, oasis_normal_test$oasis_predicted_recalib_null, digits = 2)
SMR (oasis_over_test$diedinhospital, oasis_over_test$oasis_predicted_recalib_null, digits = 2)
SMR (oasis_obese_test$diedinhospital, oasis_obese_test$oasis_predicted_recalib_null, digits = 2)
SMR (oasis_morbid_test$diedinhospital, oasis_morbid_test$oasis_predicted_recalib_null, digits = 2)



```

## Making the Calibration belt
https://cran.r-project.org/web/packages/givitiR/vignettes/givitiR.html

```{r calibration belt}

#some transformations to make the Calibration belt

apache_test_set$diedinhospital<-as.numeric(as.character(apache_test_set$diedinhospital))

oasis_test_set$diedinhospital<-as.numeric(as.character(oasis_test_set$diedinhospital))



library(givitiR)

#calibration plot for APACHE IV

data("apache_test_set")
cb <- givitiCalibrationBelt(o = apache_test_set$diedinhospital, 
                            e = apache_test_set$predictedhospitalmortality,
                            devel = "external") #the model has been developed on an external sample(external).
plot(cb, main = "APACHE IV calibration (AIV)",
                          xlab = "APACHE IV predicted probability",
                          ylab = "Observed mortality")

#calibration plot for OASIS

data ("oasis_test_set")
cb <- givitiCalibrationBelt(o = oasis_test_set$diedinhospital, 
                            e = oasis_test_set$oasis_prob,
                            devel = "external") #the model has been developed on an external sample(external).
plot(cb, main = "OASIS calibration (OASIS)",
                          xlab = "OASIS predicted probability",
                          ylab = "Observed mortality")

#calibration plot for APACHE IV recalibrated (r-AIV)

data ("apache_test_set")
cb <- givitiCalibrationBelt(o = apache_test_set$diedinhospital, 
                            e = apache_test_set$apache_predicted_recalib_null,
                            devel = "internal") #the model has been fit on the same dataset underevaluation(internal)
plot(cb, main = "APACHE IV recalibrated (r-AIV) ",
                          xlab = "APACHE IV recalibrated predicted probability",
                          ylab = "Observed mortality")


#calibration plot for APACHE IV recalibrated by BMI group (r-AIV-BMI)

data ("apache_test_set")
cb <- givitiCalibrationBelt(o = apache_test_set$diedinhospital, 
                            e = apache_test_set$apache_predicted_recalib,
                            devel = "internal") #the model has been fit on the same dataset underevaluation(internal)
plot(cb, main = "APACHE IV recalibrated with BMI  (r-AIV-BMI) ",
                          xlab = "APACHE IV recalibrated by BMI group predicted probability",
                          ylab = "Observed mortality")


#calibration plot for OASIS recalibrated (r-OASIS)

data ("oasis_test_set")
cb <- givitiCalibrationBelt(o = oasis_test_set$diedinhospital, 
                            e = oasis_test_set$oasis_predicted_recalib_null,
                            devel = "internal") #the model has been fit on the same dataset underevaluation(internal)
plot(cb, main = "OASIS recalibrated  (r-OASIS) ",
                          xlab = "OASIS recalibrated predicted probability",
                          ylab = "Observed mortality")


#calibration plot for OASIS recalibrated by BMI group (r-OASIS-BMI)

data ("oasis_test_set")
cb <- givitiCalibrationBelt(o = oasis_test_set$diedinhospital, 
                            e = oasis_test_set$oasis_predicted_recalib,
                            devel = "internal") #the model has been fit on the same dataset underevaluation(internal)
plot(cb, main = "OASIS recalibrated with BMI (r-OASIS-BMI) ",
                          xlab = "OASIS recalibrated by BMI group predicted probability",
                          ylab = "Observed mortality")

```




